Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2025-02-17 paper.tex
WIP appendices

\begin{equation}
  H_{k,N} = 1 - \frac{k_L}{k} \left| \frac{\varepsilon_L \sin{\psi}}{\left(1 + \varepsilon_L \cos{\psi}\right)^2} \right|
\end{equation}

\begin{equation}
  H_{g} = 1 - \frac{k_L}{k} \left| \frac{\varepsilon_L \sin{\psi}}{\left(1 - \varepsilon_L^2 \cos^2{\psi}\right)} \right|
\end{equation}

\begin{equation}
  S_{k,N} = 1 - \frac{\sigma_L}{\sigma} \left| \frac{\varepsilon_L \sin{\psi}}{\left(1 + \varepsilon_L \cos{\psi}\right) \sqrt{1 - \varepsilon_L^2 \cos^2{\psi}}} \right|
\end{equation}

\begin{equation}
  S_{g} = 1 - \frac{\sigma_L}{\sigma} \left| \frac{\varepsilon_L \sin{\psi}}{\left(1 - \varepsilon_L \cos{\psi}\right) \sqrt{1 - \varepsilon_L^2 \cos^2{\psi}}} \right|
\end{equation}

>>>>

\begin{equation}
  H_{k,N} = 1 - \frac{k_L}{k} \left| \frac{\varepsilon_L \sin{\psi}}{\left(1 + \varepsilon_L \cos{\psi}\right)^2} \right|
  \label{eq:homogeneity_k}
\end{equation}

\begin{equation}
  H_{g} = 1 - \frac{k_L}{k} \left| \frac{\varepsilon_L \sin{\psi}}{\left(1 - \varepsilon_L^2 \cos^2{\psi}\right)} \right|
  \label{eq:homogeneity_g}
\end{equation}

\begin{equation}
  S_{k,N} = 1 - \frac{\sigma_L}{\sigma} \left| \frac{\varepsilon_L \sin{\psi}}{\left(1 + \varepsilon_L \cos{\psi}\right) \sqrt{1 - \varepsilon_L^2 \cos^2{\psi}}} \right|
  \label{eq:stationarity_k}
\end{equation}

\begin{equation}
  S_{g} = 1 - \frac{\sigma_L}{\sigma} \left| \frac{\varepsilon_L \sin{\psi}}{\left(1 - \varepsilon_L \cos{\psi}\right) \sqrt{1 - \varepsilon_L^2 \cos^2{\psi}}} \right|
  \label{eq:stationarity_g}
\end{equation}
Notice that the steady, linearised solutions depend on both the the wavenumber
ratio $k_L/k$ and the long-wave steepness $\varepsilon_L$.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_homogeneity_stationarity_analytical.pdf}
\caption{
Homogeneity (left) and stationarity (right) of the short-wave wavenumber (top)
and effective gravity (bottom) as a function of the long-wave steepness
$\varepsilon_L$ and the wavenumber ratio $k/k_L$, based on the linearised
solutions (\ref{eq:homogeneity_k}-\ref{eq:stationarity_g}).
}
\label{fig:homogeneity_stationarity_analytical}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_homogeneity_stationarity_numerical.pdf}
\caption{
Homogeneity (left) and stationarity (right) of the short-wave wavenumber (top),
action (middle), and effective gravity (bottom) as a function of the long-wave
steepness $\varepsilon_L$ and the wavenumber ratio $k/k_L$, based on the
numerical solutions of the full wave crest and action conservation equations.
Note that the color ranges are different than those in Fig. \ref{fig:homogeneity_stationarity_analytical}.
}
\label{fig:homogeneity_stationarity_numerical}
\end{figure}
